\documentclass[a4paper,12pt]{article}
\parindent 0pt      % sets leading space for paragraphs
\usepackage{listings}

\begin{document}

\title{Getting Started with CUT}
\author{Sergei Gnezdov}
\date{\today}
\maketitle

\section{Introduction}

Cut is a unit testing framework for C, C++ and Objective-C.  This
document covers version 2.3 of CUT.  Our goal is to help you to get
started with CUT.

To download CUT, go to http://www.falvotech.com/projects/cut.php .

\section{Getting Ready}

Cut comes in source code form.  You will have to compile it to start
using.  You should have no problem to compile it on BSD (FreeBSD) or
Linux machines.

To compile run
\begin{verbatim}
  make
\end{verbatim}
command without arguments.  This should create \verb|cutgen| application.

\section{Test Driven Development in C with CUT}

\subsection{Overview}

To show the usage of CUT we will create a very simple C project.
You will have to create a directory for your project.  It is
referenced as Project directory further on.  The directory will
contain the following files:

\begin{itemize}
\item Makefile
\item Main.c
\item Compute.h
\item TestCompute.c
\item Compute.c
\item cut.h
\end{itemize}

\subsection{Creating Makefile}

Create Makefile with the following content:

\lstinputlisting{Makefile.tex}

\subsection{Defining Sum Function}

Compute.h header defines a function we want to test:

\lstinputlisting{Compute.h}

\subsection{Creating Test Case}

For consistency, the test file name is based on the name of the header
file beeing tested.  Append Test prefix and replace h with c
extension.  TestCompute.c file has the following content:

\lstinputlisting{TestCompute.c}

TestCompute.c does not compile yet.  See it for yourself with the
following command:
\begin{verbatim}
  make TestCompute.o
\end{verbatim}
The compileation fails because the compiler can't find cut.h file.
Copy cut.h file from the cut-2.3 project directory into our project
directory.

Run 
\begin{verbatim}
  make TestCompute.o
\end{verbatim}
again.  This should create TestCompute.o file.

\section{Implementing sum Function}

Create Compute.c file:

\lstinputlisting{Compute1.c}

Run 
\begin{verbatim}
  make test 
\end{verbatim}
now.  It should fail with the message similar to the following:
\begin{verbatim}
  TestCompute.c(7): Check sum
  TestCompute.c(7): Failed expression: 3 == sum(1,2)
\end{verbatim}
This is because we did not implement sum function yet.

Change Compute.c to contain the following code:

\lstinputlisting{Compute.c}

and run \verb/make test/ again.  The test should pass now.

\subsection{Creating main application}

Since our function operates as expected we can create a main
application now:

\lstinputlisting{Main.c}

Run \verb/make application/ to see the result.

\end{document}
